Bayesian Modeling and Test Planning for Multi-phase Reliability Assessment

### 2018-01-31 Final_Draft.tex
added final draft

\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, fullpage, bbm}
\usepackage{array}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{color}
%\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

@@

%AGW: I just changed the margins and spacing to
%make things easier to proofread. Uncomment the following and
%comment out the doublespacing command below.
% DON'T change margins - should be 1 inch all around.
%\addtolength{\oddsidemargin}{-.5in}%
%\addtolength{\evensidemargin}{-.5in}%
%\addtolength{\textwidth}{1in}%
%\addtolength{\textheight}{-.3in}%
%\addtolength{\topmargin}{-.8in}%

@@

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

@@

\section{Data}
Eight vehicle prototypes were used for reliability, availability, and maintainability (RAM) testing of the JLTV. There were four two-seat utility vehicles,
two four-seat general purpose vehicles, a two-seat heavy guns carrier, and a
two-seat close combat weapons carrier. The close combat weapons carrier, one
general purpose, and two utility vehicles were tested in Aberdeen, Maryland, and the heavy weapons carrier, one general purpose, and two utility vehicles
were tested in Yuma, Arizona. When comparing the test sites, the Maryland test site is much colder in the winter months but the terrain is not as harsh; in Arizona, it is warmer but with more challenging terrain. Using two test sites allows for the system to be tested under a broader range of environmental conditions.
The vehicles were driven roughly 3000 to 5000 miles in Phase 1, between
4500 and 7500 miles in Phase 2, and between 5000 and 6700 miles in Phase
3.\footnote{The exact mileage has been altered to protect proprietary information.}

@@

\subsubsection{Fix Effectiveness}\label{FEF}
After the first CAP, the second test phase begins with repaired vehicles. To plan for the reliability improvement caused by
these repairs, the PM2 reliability growth model \cite{ref2} is often used.
This model explicitly captures testing phases, choices about which failure modes
to correct, and the potential of not completely eliminating a failure upon
repair. One of the features of PM2 is that many parameters of potential
interest, such as the Fix Effectiveness Factor (FEF), which measures how much
repairs improve failure rates, are typically fixed, as PM2 is often used as a planning model. A common value for FEF is
0.70. We follow the premise of this type of model, but allow a more flexible and
data-driven result.

@@

\subsubsection{Distributional Assumption}
The next modeling choice that must be made is selecting an appropriate
probability model. This includes a selecting a sampling distribution for the data
and prior distributions for each parameter on which the sampling distribution
depends. Some common distributional choices for lifetime data are exponential, Weibull, lognormal, gamma, inverse
Gaussian, and normal failure time models.  Because all of these distributions
have a rate parameter (sometimes called a scale parameter, which is the reciprocal of the rate parameter) they can be applied in
the proposed modeling structure. We focus on the
exponential and Weibull distributions, which are commonly used for reliability.

The exponential model has probability density function
\begin{equation*}
    f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}y_{ijk})
\end{equation*}

@@

When a failure occurs during a testing phase, the mileage is recorded and the system is restored to full operation, often by repairing or replacing a component.  One must consider how these changes will affect the system reliability moving forward.  In repairable system literature, two common modeling assumptions are the extreme cases ``good as new" or ``bad as old".  ``Good as new" assumes that a repaired component has returned to a brand-new state or, in our case, that the mileage is set to zero.  On the other hand, ``bad as old" assumes the component has returned to the state it was at before the failure occurred.  The Weibull distribution implies we assuming ``bad as old" intra-test repairs by modeling the actual failure mileage $t_{ijk}$ instead of the miles between failures $y_{ijk}$.  This distinction is important in the Weibull case because the failure rate is not constant in time.  In the JLTV case study we have assumed ``bad as old" intra-test repairs based on input from subject matter experts.  There will be applications where repairs should be treated as somewhere between ``good as new" and ``bad as old".  This requires more complex modeling that is beyond the scope of this paper.  An overview of repairable system models can be found in Hamada et al. ~\cite{ref4}

We index both $\rho$ and
$\gamma$ only by $j$ and not $i$. In other words, we are assuming a single
shape and between phase adjustment parameter for each failure mode across
vehicles.  All of these parameters could also be indexed by $i$ and modeled
hierarchically or we could use a combination of common and ``related".  When failure modes do not occur within the testing period, resulting in a single censored observation, this can lead to convergence issues.  In the case study, we found 6 of the 26 failure modes had less than 10 observed (non-censored) failures across all 3 phase and 8 vehicle types.  These failure modes were attributed to system components such as the engine and armor.  To improve convergence we have binned these rare failure modes into a single "other" failure mode.  This is also useful for future testing in the case of observing failures not originally accounted for.

@@

We also consider a more formal diagnostic tool, the Deviance information criterion (DIC)
~\cite{ref5}. This is a popular method for comparing the goodness of fit of
multiple models. The DIC method includes a penalty term that grows with the
numbers of unknown parameters in the model.  The DIC is unitless, with smaller values indicating a better fit to the data.  Table~\ref{table:ta1} shows the DIC results for the different distribution and structure combinations we considered for the case study. The results show that the hierarchical Weibull model fits the data much better than the exponential or common rate models.

\begin{table}[h]
\centering
\begin{tabular}{|l|l|r|}
\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
\cline{1-3}
Distribution    & Structure & DIC \\
\hline
Exponential   & Common Rate Model                     & 21,264.19             \\
              & Hierarchical Rate Model               & 21,244.47             \\
Weibull       & Common Rate Model                     & 20,658.25             \\
              & Hierarchical Rate Model               & \textbf{17,908.06}    \\
\hline
\end{tabular}
\caption{JLTV DIC Results}
\label{table:ta1}
\end{table}

@@

We used the final exponential and Weibull models with the lowest DIC to simulate 5,000 new datasets for vehicles tested over the same number of miles for each of the three phases. We plot the resulting distributions for each of the 8 vehicles for all 3 phases. Figure~\ref{fig:test} shows two examples of the boxplots produced for one of the vehicle types, one plot from the exponential model
(left) and one plot from the Weibull model (right), with the dashed line showing
where the value from the observed dataset fell. If the model fits reasonably well, we expect to see the value from the observed data falling within the support of the simulated data. This suggests that the Weibul model fits the case study data better than the exponential data.

\begin{figure}[h!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{PPExpo}
  %\caption{}
  %\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{PPWeibull}
  %\caption{}
  %\label{fig:sub2}
\end{subfigure}
\caption{Posterior Predictive Plots \\ Exponential vs. Weibull}
\label{fig:test}
\end{figure}

\subsubsection{Case Study Results}
We have introduced several models structures and distributional assumptions that accompany them.  Using Markov chain Monte Carlo (MCMC), we fit each of these models to the JLTV case study
dataset. (The likelihoods and sampling distributions are available in the appendix.) We use the posterior distributions to estimate reliability-related quantities of interest for each of the eight vehicle types.  We are able to examine a number of different summaries related to reliability at both the component and system level.

In this study, one quantity of interest is mean miles to failure (MMTF). This is different than the commonly used mean miles between failures (MMBF).  Due to the failure rate changing over time in the Weibull case MMBF depends on how many miles the vehicle is driven.  Instead MMTF can be thought of as the average time until the first failure occurs. Figure~\ref{fig:MMTF Results} shows box plots and summary statistics from the posterior distributions of the expected miles to failure for one of the vehicle types for each of the three phases using the exponential model (left) and the more general Weibull model (right).

@@

Figure~\ref{fig:CAP} shows the posterior distributions for each of the CAP parameters $\rho_{j}^{P2}$ and $\rho_{j}^{P3}$ for the hierarchical Weibull model.  These parameters were introduced in Section~\ref{FEF}.  They are multiplicative parameters added in between phases to capture the change in failure rate due to improvements by the producer.  Values less than one indicate a decrease in failure rate.  The distributions look reasonable with most of the mass close to the commonly used FEF value of 0.70.  We notice a trend of more improvement in the second CAP between phase two and three compared to the first CAP between phase one and two.

@@

\subsubsection{Classical Approach}
In the classical (frequentist) test planning setting the risk criteria
are as follows. The \emph{producer's risk} is defined as the probability of
failing the test under the null hypothesis $\pi = \pi_0$, and the
\emph{consumer's risk} is defined as the probability of passing the test under an
alternative hypothesis $\pi = \pi_1$.  Suppose that we specify a maximum value,
$\alpha_c$, of the producer's risk and a maximum value, $\beta_c$, of the consumer's
risk. For test planning, these criteria become
$$
\begin{aligned}
	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\ &=
	P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha_c
\end{aligned}
$$
and
$$
\begin{aligned}
	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\ &=
	P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta_c
\end{aligned}
$$
To choose a test plan for specified values of $(\alpha, \pi_0, \beta, \pi_1)$,
we assume a distributional form that defines the relationship between the number
of system failures $W(t)$ and the reliability $\pi$.  We then find
the combinations of time on test and allowed failures that satisfy the risk constraints by simultaneously solving these two equations.  In the case where the component failure times are assumed to be exponentially distributed with rate parameter $\lambda_i$, the failure counts for
each component come from a homogeneous Poisson process $w_i(t) \sim
\text{Poisson}(\lambda_i t)$, and the system failure counts from $W(t) \sim
\text{Poisson}(\lambda_S t)$.  Numerous textbooks provide additional details of
this classical test planning approach. ~\cite{ref8}

@@

$$
\begin{aligned}
	 P(\lambda^* \geq \pi_0 \; \vert \; W = 0) &= \frac{
	 \int_{\pi_0}^{\infty} 1 - \exp(- \sum_i \gamma_i \lambda_i
	 T^{\gamma_i})p(\lambda_{1,...}) p(\gamma_{1,...}) d\lambda_{1,...}
	 d\gamma_{1,...}} {\int_{0}^{\infty} 1 - \exp(- \sum_i \gamma_i \lambda_i
	 T^{\gamma_i})p(\lambda_{1,...}) p(\gamma_{1,...}) d\lambda_{1,...}
	 d\gamma_{1,...}} \\
   &\approx \frac{\sum_{j = 1}^{N} 1 - \exp(-\sum_i \gamma_i^{(j)}
   \lambda_i^{(j)} T^{\gamma_i^{(j)}}) I(\lambda^* \geq \pi_0)} {\sum_{j = 1}^{N} 1 - \exp(- \sum_i
   \gamma_i^{(j)} \lambda_i^{(j)} T^{\gamma_i^{(j)}})}
\end{aligned}
$$
\\
Again we set $c = 0$ and use $N$ posterior draws for both $\lambda_i^{(j)}$ and
$\gamma_i^{(j)}$.

@@

\subsubsection{Case Study Test Plan Results}
The first step in applying this method to our case study is defining $\pi_0$,
$\pi_1$, $\alpha_b$ and $\beta_b$, which are the ARL, RRL, acceptable producer risk
and acceptable consumer risk respectively.  With input from subject matter
experts,  we will define the producer's target as the average number of
failures in the first 10,000 miles to be less than 155, and the consumer's minimum
requirements as the average number of failures in the first 10,000 miles to
greater than 175. The producer's targets and consumer's minimum requirements represent our cut off levels ARL and RRL respectively.  This means if the true average number of failures in the first 10,000 miles is less than 155 the producer would expect his product to fail the test a small proportion of the time, $\alpha_b$.  On the other hand, if the true average number of failures in the first 10,000 miles is greater than 175 the consumer would expect the product to pass the test a small proportion of the time, $\beta_b$. We will use $\alpha_b = 0.1$ and $\beta_b = 0.05$, and in practice these values should always be set based on
the true risk tolerances of the consumer and producers.  This gives us the
following probability statements to satisfy when designing the test:
\\
$$
\begin{aligned}
  \text{Consumer Risk} &: P(\sum_i 10,000^{\gamma_i} \lambda_i \geq 175 \; \vert \text{Test Is Passed}) \leq 0.1  \\
  \text{Producer Risk} &: P(\sum_i 10,000^{\gamma_i} \lambda_i \leq 155 \; \vert \; \text{Test Is Failed}) \leq 0.05
\end{aligned}
$$

@@

\begin{table}[h]
\center
\begin{tabular}{|c|c|c|}
\multicolumn{3}{c}{\textbf{Test Plans}} \\
\cline{1-3}
Failures & Assurance Test Plan & Classical Test Plan \\
Allowed & Miles Required & Miles Required \\
  & $\alpha_b$ = 0.1, $\beta_b$ = 0.05 & $\alpha_c$ = 0.1, $\beta_c$ = ? \\
\hline
1   & 240 & 225  ($\beta_c$ = 0.86) \\
2   & 250 & 305  ($\beta_c$ = 0.85) \\
3   & 260 & 385  ($\beta_c$ = 0.84) \\
4   & 275 & 460  ($\beta_c$ = 0.83) \\
5   & 290 & 530  ($\beta_c$ = 0.82) \\
\hline
\end{tabular}
\caption{Test Plan Comparison}
\label{table:ta}
\end{table}

Table 2 compares the resulting test plans of our proposed method to the classical method.  In the classical case we only controlled for the consumer's risk, because with the proposed values of  $\pi_0$, $\pi_1$, $\alpha_c$ and allowed failures there was no test mileage that would satisfy both risk criteria.  Notice this leads to extremely high levels of producer risk under the classical plan.  In general, we warn against making this comparison of test plans, because each method makes different assumptions and the test plan probability constraints are asking different questions.  The classical plan assumes product is either acceptable or unacceptable and then controls the probability of error in each of those cases.  On the other hand, the Bayesian plan puts constraints on the probability of error when the test is passed and failed.

We have provided one example where there was no solution that satisfied all of the constraints using the classical method.
This problem does not only come up using the classical method.  Both test planning approaches rely heavily on setting reasonable values for $\pi_0$, $\pi_1$, $\alpha$ and $\beta$.   When these are set to unrealistic values both procedures can result in no plan that satisfies the probability statements. ~\cite{ref9}

@@

%%%%% ref %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}
\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition 1982.
\bibitem{ref2} P.\ M.\ Ellner, J.\ B.\ Hall. An approach to reliability
growth planning based on failure mode discovery and correction using AMSAA
projection methodology. \textit{IEEE Proceedings of the Annual Reliability and
Maintainability Symposium} 2006.
\bibitem{ref3} National Research Council. Statistics, Testing, and Defense
Acquisition: Background Papers. \textit{National Academies Press} 1999.
\bibitem{ref4} M.\ Hamada, A.\  Wilson, C.\ Reese, H.\ Martz. Bayesian Reliability. Springer 2008.
\bibitem{ref5} D.\  Spiegelhalter, N.\ Best, B.\ Carlin, A.\ Van der
Linde Bayesian measures of model complexity and fit. \textit{Royal Statistical
Society}, Series B, 64: 583-640 2002.
\bibitem{ref6} A. Gelman, M. Xiao-Li, H. Stern. Posterior predictive assessment of model fitness via realized discrepancies (with discussion). \textit{Statist. Sin.} 6, 733-807 1996.
\bibitem{ref7} W.\ Meeker, L.\ Escobar. Reliability: the other
dimension of quailty. \textit{Quality Technology and Quantitative Management} 1, 1-25 2004.
\bibitem{ref8} J.\ F.\ Lawless. Statistical Models and Methods for Lifetime Data, 2nd Edition. John Wiley \& Sons 2011.
\bibitem{ref9} B.\ Weaver, M.\ Hamada, A.\ Wilson, J.\ Bakerman. Bayesian Assurance Tests for Degradation Data. \textit{Quality and Reliability Engineering International} 33(8): 2699-2709  2017.
\end{thebibliography}

@@

Full conditionals for Gibbs sampling:
\begin{align*}
\lambda_i|\cdot &\sim \text{Gamma}(n_i + \alpha, \sum_{j=1}^{n_i}y_{ij}p^* + \beta) \\
\beta|\cdot &\sim \text{Gamma}(8\alpha + b_1, \sum{\lambda_i} + b_2) \\
\rho^{P2}|\cdot &\sim \text{Gamma}(N_{1,2} + c_1, \sum{y_{ij}\lambda_i} + c_2) \\
\rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{y_{ij}\lambda_i} + d_2) \\
\alpha|\cdot &\sim \prod_{i = 1}^8 \Bigg[\prod_{j =1}^R \frac{\beta^\alpha}{\Gamma(\alpha)}\lambda_i^{\alpha -
  1}\Bigg] (\alpha^{a_1-1}e^{-\alpha a_2}) \text{(Metropolis-Hastings used for sampling)}
\end{align*}

@@

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, fullpage, bbm, float}
\usepackage{array}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{color}
%\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL
\renewcommand{\vec}[1]{\mathbf{#1}}

@@

%AGW: I just changed the margins and spacing to
%make things easier to proofread. Uncomment the following and
%comment out the doublespacing command below.
% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%

@@

% \def\spacingset#1{\renewcommand{\baselinestretch}%
% {#1}\small\normalsize} \spacingset{1}

@@

\section{Data}
Eight vehicle prototypes were used for reliability, availability, and maintainability (RAM) testing of the JLTV. There were four two-seat utility vehicles,
two four-seat general purpose vehicles, a two-seat heavy guns carrier, and a
two-seat close combat weapons carrier. The close combat weapons carrier, one
general purpose, and two utility vehicles were tested in Aberdeen, Maryland, and the heavy weapons carrier, one general purpose, and two utility vehicles
were tested in Yuma, Arizona. When comparing the test sites, the Maryland test site is much colder in the winter months but the terrain is not as harsh; in Arizona, it is warmer but with more challenging terrain. Using two test sites allows for the system to be tested under a broader range of environmental conditions.
The vehicles were driven roughly 3000 to 5000 miles in Phase 1, between
4500 and 7500 miles in Phase 2, and between 5000 and 6700 miles in Phase
3. The actual mileage we use in our case study has been altered to protect proprietary information.

@@

\subsubsection{Fix Effectiveness}\label{FEF}
After the first CAP, the second test phase begins with repaired vehicles. To plan for the reliability improvement caused by
these repairs, the PM2 reliability growth model \cite{ref2} is often used.
This model explicitly captures testing phases, choices about which failure modes
to correct, and the potential of not completely eliminating a failure upon
repair. Since PM2 is used for planning, many parameters of potential
interest are assumed fixed. An example is the Fix Effectiveness Factor (FEF), which measures how much
repairs improve failure rates. A common value for FEF is
0.70. We follow the premise of this type of model, but allow a more flexible and
data-driven result.

@@

\subsubsection{Distributional Assumption}
The next modeling choice that must be made is selecting an appropriate
probability model. This includes a selecting a sampling distribution for the data
and prior distributions for each parameter on which the sampling distribution
depends. Some common distributional choices for lifetime data are exponential, Weibull, lognormal, gamma, inverse
Gaussian, and normal failure time models.  Because all of these distributions
have a rate parameter (sometimes called a scale parameter, which is the reciprocal of the rate parameter), they can be applied in
the proposed modeling structure. We focus on the
exponential and Weibull distributions, which are commonly used for reliability.

The exponential model has probability density function
\begin{equation*}
    f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}y_{ijk}) \;.
\end{equation*}

@@

When a failure occurs during a testing phase, the mileage is recorded and the system is restored to full operation, often by repairing or replacing a component.  One must consider how these changes will affect the system reliability moving forward.  In repairable system literature, two common modeling assumptions are the extreme cases ``good as new" or ``bad as old".  ``Good as new" assumes that a repaired component has returned to a brand-new state or, in our case, that the mileage is set to zero.  On the other hand, ``bad as old" assumes the component has returned to the state it was at before the failure occurred.  The Weibull distribution implies we assuming ``bad as old" intra-test repairs by modeling the actual failure mileage $t_{ijk}$ instead of the miles between failures $y_{ijk}$.  This distinction is important in the Weibull case because the failure rate is not constant in time.  In the JLTV case study we have assumed ``bad as old" intra-test repairs based on input from subject matter experts.  There will be applications where repairs should be treated as somewhere between ``good as new" and ``bad as old".  This requires more complex modeling that is beyond the scope of this paper.  An overview of Bayesian approaches for repairable system models can be found in Hamada et al. ~\cite{ref4}

We index both $\rho$ and
$\gamma$ only by $j$ and not $i$. In other words, we are assuming a single
shape and between phase adjustment parameter for each failure mode across
vehicles.  All of these parameters could also be indexed by $i$ and modeled
hierarchically or we could use a combination of common and ``related".  When failure modes do not occur within the testing period, resulting in a single censored observation, this can lead to convergence issues.  In the case study, we found 6 of the 26 failure modes had less than 10 observed (non-censored) failures across all 3 phase and 8 vehicle types.  These failure modes were attributed to system components such as the engine and armor.  To improve convergence we have binned these rare failure modes into a single ``other" failure mode.  This may also be useful for planning future testing to account for previously unobserved failure modes.

@@

We also consider a more formal diagnostic tool, the deviance information criterion (DIC)
~\cite{ref5}. This is a popular method for comparing the goodness of fit of
multiple models. The DIC method includes a penalty term that grows with the
numbers of unknown parameters in the model.  The DIC is unitless, with smaller values indicating a better fit to the data.  Table~\ref{table:ta1} shows the DIC results for the different distribution and structure combinations we considered for the case study. The results show that the hierarchical Weibull model fits the data much better than the exponential or common rate models.

@@

We used the final exponential and Weibull models with the lowest DIC to simulate 5,000 new datasets for vehicles tested over the same number of miles for each of the three phases. We plot the resulting distributions for each of the 8 vehicles for all 3 phases. Figure~\ref{fig:test} shows two examples of the boxplots produced for one of the vehicle types, one plot from the exponential model
(left) and one plot from the Weibull model (right), with the dashed line showing
where the value from the observed dataset fell. If the model fits reasonably well, we expect to see the value from the observed data falling within the support of the simulated data. This suggests that the Weibull model fits the case study data better than the exponential data.

\subsubsection{Case Study Results}
We have introduced several models structures and distributional assumptions that accompany them.  Using Markov chain Monte Carlo (MCMC), we fit each of these models to the JLTV case study
dataset. (Details of the likelihoods and full conditional distributions are available in the appendix.) We use the posterior distributions to estimate reliability-related quantities of interest for each of the eight vehicle types.  We are able to examine a number of different summaries related to reliability at both the component and system level.

In this study, one quantity of interest is mean miles to failure (MMTF). This is different than the commonly used mean miles between failures (MMBF).  Due to the failure rate changing over time in the Weibull case MMBF depends on how many miles the vehicle is driven.  MMTF can be thought of as the average time until the first failure occurs. Figure~\ref{fig:MMTF Results} shows box plots and summary statistics from the posterior distributions of the expected miles to first failure for one of the vehicle types for each of the three phases using the exponential model (left) and the more general Weibull model (right).

@@

Figure~\ref{fig:CAP} shows the posterior distributions for each of the CAP parameters $\rho_{j}^{P2}$ and $\rho_{j}^{P3}$ for the hierarchical Weibull model.  These parameters were introduced in Section~\ref{FEF}.  They are multiplicative parameters added in between phases to capture the change in failure rate due to improvements by the producer.  Values less than one indicate a decrease in failure rate. Interestingly, the distributions have most of their mass close to the commonly used FEF value of 0.70.  We notice a trend of more improvement in the second CAP between phase two and three as compared to the first CAP between phase one and two.

@@

\subsubsection{Classical Approach}\label{sec321:ca}
In the classical (frequentist) test planning setting the risk criteria
are as follows. The \emph{producer's risk} is defined as the probability of
failing the test under the null hypothesis $\pi = \pi_0$, and the
\emph{consumer's risk} is defined as the probability of passing the test under an
alternative hypothesis $\pi = \pi_1$.  Suppose that we specify a maximum value,
$\alpha_c$, of the producer's risk and a maximum value, $\beta_c$, of the consumer's
risk. For test planning, these criteria become
$$
\begin{aligned}
	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\ &=
	P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha_c
\end{aligned}
$$
and
$$
\begin{aligned}
	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\ &=
	P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta_c
\end{aligned}
$$
To choose a test plan for specified values of $(\alpha, \pi_0, \beta, \pi_1)$,
we assume a distributional form that defines the relationship between the number
of system failures $W(t)$ and the reliability $\pi$.  We then find
the combinations of time on test and allowed failures that satisfy the risk constraints by simultaneously solving these two equations.  In the case where the component failure times are assumed to be exponentially distributed with rate parameter $\lambda_i$, the failure counts for
each component come from a homogeneous Poisson process $w_i(t) \sim
\text{Poisson}(\lambda_i t)$, and the system failure counts from $W(t) \sim
\text{Poisson}(\lambda_S t)$.  Numerous textbooks (e.g., \cite{ref8}) provide additional details of
this classical test planning approach.

@@

$$
\begin{aligned}
	 P(\lambda^* \geq \pi_0 \; \vert \; W = 0) &= \frac{
	 \int_{\pi_0}^{\infty} 1 - \exp(- \sum_i \gamma_i \lambda_i
	 T^{\gamma_i})p(\vec{\lambda}) p(\vec{\gamma}) d\vec{\lambda}
	 d\vec{\gamma}} {\int_{0}^{\infty} 1 - \exp(- \sum_i \gamma_i \lambda_i
	 T^{\gamma_i})p(\vec{\lambda}) p(\vec{\gamma}) d\vec{\lambda}
	 d\vec{\gamma}} \\
   &\approx \frac{\sum_{j = 1}^{N} 1 - \exp(-\sum_i \gamma_i^{(j)}
   \lambda_i^{(j)} T^{\gamma_i^{(j)}}) I(\lambda^* \geq \pi_0)} {\sum_{j = 1}^{N} 1 - \exp(- \sum_i
   \gamma_i^{(j)} \lambda_i^{(j)} T^{\gamma_i^{(j)}})}
\end{aligned}
$$
\\
where $\vec{\lambda}$ and $\vec{\gamma}$ denote the vectors of $\lambda_i$ and $\gamma_i$. Again we set $c = 0$ and use $N$ posterior draws for both $\lambda_i^{(j)}$ and
$\gamma_i^{(j)}$.

@@

\subsubsection{Case Study Test Plan Results}
The first step in applying the Bayesian assurance test planning method to our case study is defining $\pi_0$,
$\pi_1$, $\alpha_b$ and $\beta_b$, which are the ARL, RRL, acceptable producer risk
and acceptable consumer risk respectively.  With input from subject matter
experts,  we will define the producer's target as the average number of
failures in the first 10,000 miles to be less than 155, and the consumer's minimum
requirements as the average number of failures in the first 10,000 miles to
greater than 175. The producer's targets and consumer's minimum requirements represent our cut off levels ARL and RRL respectively.  This means if the true average number of failures in the first 10,000 miles is less than 155 the producer would expect his product to fail the test a small proportion of the time, $\alpha_b$.  On the other hand, if the true average number of failures in the first 10,000 miles is greater than 175 the consumer would expect the product to pass the test a small proportion of the time, $\beta_b$. We will use $\alpha_b = 0.1$ and $\beta_b = 0.05$, and in practice these values should always be set based on
the true risk tolerances of the consumer and producers.  This gives us the
following probability statements to satisfy when designing the test:
\\
$$
\begin{aligned}
  \text{Consumer Risk} &: P(\sum_i 10,000^{\gamma_i} \lambda_i \geq 175 \; \vert \text{Test Is Passed}) \leq 0.1  \\
  \text{Producer Risk} &: P(\sum_i 10,000^{\gamma_i} \lambda_i \leq 155 \; \vert \; \text{Test Is Failed}) \leq 0.05
\end{aligned}
$$

@@

Table 2 compares the resulting test plans of our proposed method to the classical method. In general, we warn against making this comparison of test plans, because as we discuss below, each method makes different assumptions and the test plan probability constraints are addresses different questions.

As is common in DoD test planning, for the classical case we only controlled for the consumer's risk, not for both risks as described in Section~\ref{sec321:ca}. Notice this leads to extremely high levels of producer risk under the classical plan. (Note that with the proposed values of  $\pi_0$, $\pi_1$, $\alpha_c$ and allowed failures there was no test mileage that would satisfy both classical risk criteria.) The classical plan assumes product is either acceptable or unacceptable and then controls the probability of error in each of those cases. For example, interpreting the first row of Table 1, if a system is put on test where the average number of failures in 10,000 miles is 155, the the probability of failing the test and observing two or more failures in 225 miles is 0.86. If a system is put on test where the average number of failures in 10,000 miles is 175, then the probability of passing the test and observing no more than one failure in 225 miles is 0.10.

By comparison, the Bayesian plan puts constraints on the probability of error when the test is passed and failed.  From the study, the posterior producer risk is the probability the average number of failures in 10,000 miles for the system is less than 155 given that the test is failed and two or more failures are observed in 240 miles. The posterior consumers risk is the probability that the average number of failures in 10,000 miles for the system is greater than 175 given that the test is passed by observing no more than one failure in 240 miles.

We have provided one example where there was no solution that satisfied all of the constraints using the classical method.
This problem does not only come up using the classical method.  Both test planning approaches rely heavily on setting reasonable values for $\pi_0$, $\pi_1$, $\alpha$ and $\beta$.   When these are set to unrealistic values both procedures can result in no plan that satisfies the probability statements ~\cite{ref9}.

@@

%%%%% ref %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}
\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition 1982. \url{http://www.dtic.mil/dtic/tr/fulltext/u2/a120261.pdf}
\bibitem{ref2} P.\ M.\ Ellner, J.\ B.\ Hall. An approach to reliability
growth planning based on failure mode discovery and correction using AMSAA
projection methodology. \textit{Proceedings of the Annual Reliability and
Maintainability Symposium} 2006.
\bibitem{ref3} National Research Council. Statistics, Testing, and Defense
Acquisition: Background Papers. \textit{National Academies Press} 1999.
\bibitem{ref4} M.\ Hamada, A.\  Wilson, C.\ Reese, H.\ Martz. Bayesian Reliability. Springer 2008.
\bibitem{ref5} D.\  Spiegelhalter, N.\ Best, B.\ Carlin, A.\ Van der
Linde Bayesian measures of model complexity and fit. \textit{Journal of the Royal Statistical
Society, Series B}, 64: 583-640 2002.
\bibitem{ref6} A. Gelman, M. Xiao-Li, H. Stern. Posterior predictive assessment of model fitness via realized discrepancies (with discussion). \textit{Statistica Sinica} 6, 733-807 1996.
\bibitem{ref7} W.\ Meeker, L.\ Escobar. Reliability: the other
dimension of quailty. \textit{Quality Technology and Quantitative Management} 1, 1-25 2004.
\bibitem{ref8} J.\ F.\ Lawless. Statistical Models and Methods for Lifetime Data, 2nd Edition. John Wiley \& Sons 2011.
\bibitem{ref9} B.\ Weaver, M.\ Hamada, A.\ Wilson, J.\ Bakerman. Bayesian Assurance Tests for Degradation Data. \textit{Quality and Reliability Engineering International} 33(8): 2699-2709  2017.
\end{thebibliography}

@@

Full conditionals for Gibbs sampling:
\begin{align*}
\lambda_i|\cdot &\sim \text{Gamma}(n_i + \alpha, \sum_{j=1}^{n_i}y_{ij}p^* + \beta) \\
\beta|\cdot &\sim \text{Gamma}(8\alpha + b_1, \sum{\lambda_i} + b_2) \\
\rho^{P2}|\cdot &\sim \text{Gamma}(N_{1,2} + c_1, \sum{y_{ij}\lambda_i} + c_2) \\
\rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{y_{ij}\lambda_i} + d_2) \\
\alpha|\cdot &\propto \prod_{i = 1}^8 \Bigg[\prod_{j =1}^R \frac{\beta^\alpha}{\Gamma(\alpha)}\lambda_i^{\alpha -
  1}\Bigg] (\alpha^{a_1-1}e^{-\alpha a_2}) \;\; \text{(Metropolis-Hastings used for sampling)}
\end{align*}

@@

\section{Tables}

\begin{table}[H]
\centering
\begin{tabular}{|l|l|r|}
\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
\cline{1-3}
Distribution    & Structure & DIC \\
\hline
Exponential   & Common Rate Model                     & 21,264.19             \\
              & Hierarchical Rate Model               & 21,244.47             \\
Weibull       & Common Rate Model                     & 20,658.25             \\
              & Hierarchical Rate Model               & \textbf{17,908.06}    \\
\hline
\end{tabular}
\caption{JLTV DIC Results}
\label{table:ta1}
\end{table}

\begin{table}[H]
\center
\begin{tabular}{|c|c|c|}
\multicolumn{3}{c}{\textbf{Test Plans}} \\
\cline{1-3}
Failures & Assurance Test Plan & Classical Test Plan \\
Allowed & Miles Required & Miles Required \\
  & $\alpha_b$ = 0.1, $\beta_b$ = 0.05 & $\alpha_c$ = 0.1, $\beta_c$ = ? \\
\hline
1   & 240 & 225  ($\beta_c$ = 0.86) \\
2   & 250 & 305  ($\beta_c$ = 0.85) \\
3   & 260 & 385  ($\beta_c$ = 0.84) \\
4   & 275 & 460  ($\beta_c$ = 0.83) \\
5   & 290 & 530  ($\beta_c$ = 0.82) \\
\hline
\end{tabular}
\caption{Test Plan Comparison}
\label{table:ta}
\end{table}

\section{Figures}

\begin{figure}[ht]
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{PPExpo}
\end{subfigure}%
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{PPWeibull}
\end{subfigure}
\caption{Posterior Predictive Plots \\ Exponential vs. Weibull}
\label{fig:test}
\end{figure}
